Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-08-12 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:08:12	18:15:16	(Wed12.Aug)

\IEEEPARstart{T}{he} best adaptive sonars are found in nature. Bats, for instance, use a high frequency sonar to detect, identify and track prey with amazing precision in caves amongst a myriad of other bats. In comparison, human made sonars inhibit minimal adaptability in the data collection process, but try to make up for it in the post processing of the data. Perhaps the most studied adaptive method for reconstructing a sonar image is the minimum variance distortionless response (MVDR) beamformer.

MVDR is often able to improve image contrast and resolution compared to conventional static methods~\cite{Blomberg2013,Blomberg2012a,Dursun2009,Lo2004}. However, it is computationally intensive, needs robustification to work well, and should be used on images that are oversampled 10 times in azimuth.

In prior studies we have investigated ways to reduce the complexity of MVDR and accelerate it using graphics computing units (GPUs)~\cite{Buskenes2014,Aasen2013}.

@@

One of the best studied adaptive methods is the minimum variance distortion-less response (MVDR) beamformer~\cite{Capon1969}. It computes a weight set that minimizes the power of noise and interference solves an optimization problem to come up with a weight set that yields unity gain in the desired direction, while minimizing the effect of noise and interference from other directions. The result is often good looking non-linear image with improved contrast and detail resolution. However, MVDR is neither statistically nor numerically robust by default, and typically needs to average data in space and time, and regularization. This constrains the solution space of the weights.

@@

The Minimum Variance (MV) beamformer selects the window that minimizes the beamformer's output power~\cite{cap69}. It has recently been investigated for active sonar imaging in e.g.~\cite{saf09}, and in ultrasound imaging in e.g.~\cite{syn07}. We suggest using a Low Complexity Adaptive (LCA) beamformer, which for each pixel applies a set of predefined windows and selects one of them based on the MV criterion. Using the LCA beamformer results in increased robustness and improved edge definition compared to the MV and DAS beamformers.

@@

>>>>

\IEEEPARstart{T}{he} best adaptive sonars are found in nature. Bats, for instance, use a high frequency sonar to detect, identify and track prey with amazing precision in caves amongst a myriad of other bats. In comparison, human made sonars inhibit minimal adaptability in the data collection process, but try to make up for it in the post processing of the data. Perhaps the most studied adaptive method for reconstructing a sonar image is the minimum variance distortionless response (MVDR) beamformer~\cite{Capon1969}. It computes the window that is optimal in the sense of suppressing as much energy from the noise and interference as possible.

MVDR is often able to improve image contrast and resolution compared to conventional static methods~\cite{Blomberg2013,Blomberg2012a,Dursun2009,Lo2004}. However, this comes at a cost of a computational complexity that is cubic with the number of channels, O($M^3$), while conventional beamformers are at O($M$). We have shown in previous studies that this complexity can be reduced, and the method accelerated significantly using graphics computing units (GPUs)~\cite{Buskenes2014,Asen2013}. However, in this work we propose

We suggest using a Low Complexity Adaptive (LCA) beamformer, which for each pixel applies a set of predefined windows and selects one of them based on the MV criterion. Using the LCA beamformer results in increased robustness and improved edge definition compared to the MV and DAS beamformers.

@@

However, MVDR is neither statistically nor numerically robust by default, and typically needs to average data in space and time, and regularization. This constrains the solution space of the weights.

@@

@@

oversampled 10 times in azimuth~\cite{Asen2014}.
